Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2014-03-27 parts/example.tex
describe metazoan example

\subsection{\ldots (metazoan)}

\todo{Describe the model}

\begin{example}
  The model of \pref{fig:metazoan-php} gives an example of PH with $3$ classes of priorities.
  Although the actions of the highest class of priority are only used to update a cooperative sort,
  the actions of the intermediate priority do not follow the constraints of \pref{ssec:hypothesis},
  thus having a biological meaning by representing different reaction speeds.

@@

      \path (1.8, 1.5) edge[superprio,coopupdate] (3.2, 2);
      \path (0.8, 4.5) edge[superprio,coopupdate] (3.2, 3);
    \end{tikzpicture}
    }
    \caption{
    \label{fig:metazoan-php}
      An example of PH $\oPH$ with $3$ classes of priorities.
      Actions of $\ov{\PHh}^{(3)}$ (lowest priority) are in thin lines,
      actions of $\ov{\PHh}^{(2)}$ (intermediate priority) are in thick lines,
      and actions of $\ov{\PHh}^{(1)}$ (highest priority), whose only purpose is to update the cooperative sort $fc$,
      are not represented but modeled by the double dashed arrows.
    }
  \end{figure}
\end{example}

\begin{example}
  \pref{fig:metazoan-ph} gives the flattened model of the PH of \pref{fig:metazoan-php}.
  It contains $2$ classes of priority, and prioritized actions are only used to update cooperative sorts.
  Note that according to the simplifications mentioned at the end of \pref{ssec:flattening},
  the auto-action $h_1 = \PHhit{c_1}{c_1}{c_0}$ in $\oPH$ has been flattened to a regular action $\PHhit{a_0}{c_1}{c_0}$
  because its playability property could be simplified to $\Fop{h_1} \equiv c_1 \wedge a_0 \equiv a_0$.

@@

      \path (-0.8, 1.5) edge[prio,coopupdate] (-2.2, 1.5);
      \path (4.3, 4.5) edge[prio,coopupdate] (-2.2, 2.5);
    \end{tikzpicture}
    }
    \caption{
    \label{fig:metazoan-ph}
      An example of PH $\PH$ with $2$ classes of priorities.
      Actions of $\PHh^{(2)}$ (unprioritized) are in thin lines,
      and actions of $\PHh^{(1)}$ (prioritized) which are used to update cooperative sorts,
      are abstracted by thick dashed arrows.
    }
  \end{figure}
\end{example}

\subsection{Large-scale Application}

>>>>

\subsection{Flattening of a model: Metazoan segmentation}

In this section, we illustrate the flattening method presented in \pref{ssec:flattening}
on a model of metazoan segmentation established in silico in \cite{MSB:MSB4100192}
in a differential equations framework.
It is composed of a wavefront gene $f$ that activates the gap-gene $a$ whose products are responsible or stripes.
Gene $f$ also activates a gene $c$ whose products repress the gene $a$.
The auto-inhibition of $c$ generalises a chain of repressors on $a$.
The auto-inhibition of $f$, which terminates the stripes formation in the original model,
have been removed in order to focus on the stationary dynamics of the model.

The actions of the original model make $3$ classes of priorities, as represented in \pref{fig:metazoan-php}.
Thus, although the actions of the highest class of priority are only used to update a cooperative sort,
the actions of the two other classes of priorities do have a biological meaning.
%by representing different reaction rates.
Indeed, they have been derived given the different reaction rates,
given the fact that the switches of genes $a$ and $c$ have to alternate in order not to miss a stripe.

@@

    \path (1.8, 1.5) edge[superprio,coopupdate] (3.2, 2);
    \path (0.8, 4.5) edge[superprio,coopupdate] (3.2, 3);
  \end{tikzpicture}
  }
  \caption{
  \label{fig:metazoan-php}
    An example of PH $\oPH$ with $3$ classes of priorities.
    Actions of $\ov{\PHh}^{(3)}$ (lowest priority) are in thin lines,
    actions of $\ov{\PHh}^{(2)}$ (intermediate priority) are in thick lines,
    and actions of $\ov{\PHh}^{(1)}$ (highest priority), whose only purpose is to update the cooperative sort $fc$,
    are not represented but modeled by the double dashed arrows.
  }
\end{figure}

\pref{fig:metazoan-ph} gives the flattening of this model.
It contains $2$ classes of priority, and prioritised actions are only used to update cooperative sorts.
Note that according to the simplifications mentioned at the end of \pref{ssec:flattening},
the auto-action $h_1 = \PHhit{c_1}{c_1}{c_0}$ in $\oPH$ has been flattened to a regular action $\PHhit{a_0}{c_1}{c_0}$
because its playability property could be simplified to $\Fop{h_1} \equiv c_1 \wedge a_0 \equiv a_0$.

\todo{Results on reachability?}

@@

    \path (-0.8, 1.5) edge[prio,coopupdate] (-2.2, 1.5);
    \path (4.3, 4.5) edge[prio,coopupdate] (-2.2, 2.5);
  \end{tikzpicture}
  }
  \caption{
  \label{fig:metazoan-ph}
    An example of PH $\PH$ with $2$ classes of priorities.
    Actions of $\PHh^{(2)}$ (unprioritized) are in thin lines,
    and actions of $\PHh^{(1)}$ (prioritized) which are used to update cooperative sorts,
    are abstracted by thick dashed arrows.
  }
\end{figure}

\subsection{Large-scale Application: T-cell receptor}
